Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-24 paper/eccv2020submission.tex
Addin the recursive aplication portion and the split methodoogy

\documentclass{llncs}
\usepackage[pagebackref]{hyperref}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}

@@

\subsection{Simulation Setup and Data generation}
\emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.} The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{list}{$\circ$}{}
\item Inflow condition on the left side of the channel
\item Outflow condition on the right side of the channel
\item No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{list}
The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{list}{$\circ$}{}
\item plain: a single simulation with \ldots.
\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{list}

@@

Because the number of simulations in each set is different, we also generated different number of images per simulation based on the corresponding set. For the plain dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time). For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time). For the viscosity-density model --- overall 104328 frames from 334 simulation (322 frames per simulation for 11 seconds of simulated physical time). Even though the simulation in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.

@@

\\

\begin{center}
  \begin{tabular}{l|c|c}
    Model type & Max difference &  Average difference\\
    \hline
    Constant & 0.5 &  0.5 \\
    Inflow speed &  0.5 &  0.5 \\
    Viscosity-density &  0.5  &  0.5 \\
  \end{tabular}
\end{center}

@@

\\

@@

\noindent\textbf{Recursive Application Performance:}

@@

\clearpage
\bibliographystyle{splncs04}
\bibliography{egbib}
\end{document}

>>>>

\documentclass{llncs}
\usepackage[title]{appendix}
\usepackage[pagebackref]{hyperref}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}

@@

\subsection{Simulation Setup and Data generation}
\emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.} The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{list}{$\circ$}{}
\item Inflow condition on the left side of the channel
\item Outflow condition on the right side of the channel
\item No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{list}
The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{list}{$\circ$}{}
\item constant: a single simulation with \ldots.
\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{list}

@@

Because the number of simulations in each set is different, we also generated different number of images per simulation based on the corresponding set. For the constant dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time). For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time). For the viscosity-density model --- overall 104328 frames from 334 simulation (322 frames per simulation for 11 seconds of simulated physical time). Even though the simulation in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.

After all images were generated, a test-train split was created for each of the datasets The split for the inflow speed and viscosity-density sets were done manually. For the inflow speed set, we selected every fourth simulation to be part of the test set and for the viscosity-density set --- every 25th. All other simulations are used for training. The split for the constant dataset was done at random. All of the splits result in a 80\% of the data being used for training and the rest for testing. It is important to note that all of the images in the test sets come from simulations with parameters that are not found for the simulations in the training sets. This means that the datasets are designed in a way to see if the models can generalize the parameters of the simulations and predict simulations with parameters that are unseen during the training.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{l|c|c}
      Model type & Max difference &  Average difference\\
      \hline
      Constant & 0.5 &  0.5 \\
      Inflow speed &  0.5 &  0.5 \\
      Viscosity-density &  0.5  &  0.5 \\
    \end{tabular}
  \end{center}
  \caption{\label{tab:table-name} Your caption.}
\end{table}

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/pred}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/pred.png}  
  \end{subfigure}
\end{figure}

@@

@@

\noindent\textbf{Recursive Application Performance:}
With this evaluation case we want to see how our models handle recursive application. That is, the output of the network is used again as an input for the prediction of the next simulation frame.

For each recursive evaluation we generate 40 frames of the corresponding simulation. We did not in any was post-processed the output of the networks before feeding it as an input. We calculate the discussed metrics for each of the predicted frames while comparing them to the corresponding real one.

In our experiments, we performed several recursive evaluation for each simulation while starting at frames with different index. We wanted to see how a different starting point in the simulation can affect the frames predicted by the models.

The viscosity-density and inflow speed models are evaluated with several simulations with different parameters. As it is unpracticed to give the results of the evaluation of each simulation, here we present only several of them. The showed results, however, are representative of the general performance of our models. For this section, We also limit ourselves only to models that do use the pressure field of the simulations.

The constant model is evaluated with a single simulation --- the one it was trained with. [fig] presents the results of the recursive application. During the evaluation we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation. That is, its index relative to the first frame is higher. The plots for the constant model in [fig] illustrate this.

For the inflow speed model we present the results from three different simulations in [fig]. We can see the same trend that predicting frames with smaller index is harder. We, however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly. [fig] presents the results of the viscosity-density model.

We again do not explicitly give the correlation between the predicted and real frames. In all cases the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$. The CFD-metrics are summarized in [table].

@@

\clearpage
\bibliographystyle{splncs04}
\bibliography{egbib}

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}%

\section{Networks architectures and hyperparameters}
\emph{Here we give the exact details on the architectures of the used networks.}

\end{subappendices}

\end{document}
